### 2018-08-02 article.tex
Rewriting systems as 2-PROPS: Proposition 2 / Proposition 2 corollary
Q-valued rewriting systems: Homomorphism / Remark
Q-valued rewriting systems: Proposition / Proposition corollary

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\begin{align}
r &= r_1 \circ r_2 \circ r_3 \circ \cdots \circ r_j \cr
r &= r_1 \otimes r_2 \otimes r_3 \otimes \cdots \otimes r_k
\end{align}

\begin{proof}
The proof is the same but this time we have to use
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_i
\]
Such that for all $i$
\[
r_i = r_{i, 1} \circ r_{i, 2} \circ r_{i, 3} \circ \cdots \circ r_{i, j}
\]
and for all $j$
\[
r_{i, j} = \bigotimes_k^l r_{i, j, k}
\]
a tensor products of transformations.
\end{corollary}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\catC(a, b)$ to $\mathbb{Q}$ homomorphism}

Let's define the following homomorphism $F$ from $\catC(a, b)$ to $\mathbb{Q}$. For all $f: a \to b \in \{f_i\}_i$
\[
F(f) \in L
\]
For all $r: f \Rightarrow g \in \{r_i\}_i$
\[
F(r) = F(f) \oplus F(g)^{-1}
\]

On 1-cells
\begin{align}
F(f \circ g) &\preceq F(f) \oplus F(g) \cr
F(f \otimes g) &\preceq F(f) \oplus F(g)
\end{align}

On 2-cells
\begin{align}
F(r \circ s) &= F(r) \oplus F(s) \cr
F(r \otimes s) &= F(r) \oplus F(s) \cr
F(r \bullet s) &= F(r) \oplus F(s)
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
F(r: f \Rightarrow g) = F(f) \oplus F(g)^{-1}
\]
then
\begin{align}
F(r: f \Rightarrow f) &= F(f) \oplus F(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, F(id_f) = e
\end{align}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $F(r) = F(s)$.

\begin{proof}
The set of all possible transformation is freely generated by $\{r_i\}_i$, $\bullet$, $\circ$ and $\otimes$ so both $r$ and $s$ can be written
\begin{align}
r &= r_1 \odot r_2 \odot r_3 \odot \cdots \odot r_n \cr
s &= s_1 \odot s_2 \odot s_3 \odot \cdots \odot s_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i
\begin{align}
r_i &\in \{f_i\}_i \cr
s_i &\in \{f_i\}_i
\end{align}
If $n = 1$ then $r \in \{f_i\}_i$, so $F(r) = F(f) \oplus F(g)^{-1}$.
Otherwise
\begin{align}
F(r) &= F(r_1 \odot r_2 \odot \cdots \odot r_n) \cr
&= F(r_1) \oplus F(r_2) \oplus \cdots \oplus F(r_n) \cr
&= F(f \Rightarrow h_1) \oplus F(h_1 \Rightarrow h_2) \oplus \cdots \oplus F(h_n \Rightarrow g) \cr
&= F(f) \oplus F(h_1)^{-1} \oplus F(h_1) \oplus F(h_2)^{-1} \oplus \cdots \oplus F(h_n) \oplus F(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
F(f) \oplus F(h_1)^{-1} \oplus F(h_1) \oplus F(h_2)^{-1} \oplus F(h_2) \oplus \cdots \oplus F(h_n) \oplus F(g)^{-1} = F(f) \oplus F(g)^{-1}
\]
The same is true for $s$, so
\[
F(r) = F(s) = F(f) \oplus F(g)^{-1}
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION CO           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $F(r) = F(f) \oplus F(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}
